---
title: "Statistical Analysis of CPI and Income"
output: html_notebook
---
By: Aditya Jain, Ahmed Omar, Yedu Krishnan

```{r}
library(binom)
library(car)
library(collapsibleTree)
library(dbplyr)
library(dplyr)
library(EnvStats)
library(ggformula)
library(ggplot2)
library(gmodels)
library(htmltools)
library(ISLR)
library(knitr)
library(lawstat)
library(markdown)
library(mosaic)
library(mdsr)
library(mosaicData)
library(nycflights13)
library(olsrr)
library(plyr)
library(purrr)
library(plotly)
library(resampledata)
library(rmarkdown)
library(rpart)
library(rpart.plot)
library(rvest)
library(SDaA)
library(shiny)
library(stringi)
library(tibble)
library(tidyr)
library(tidyselect)
library(tinytex)
library(yaml)
library(shiny)
```

## **Introduction**

“The Consumer Price Index (CPI) represents changes in prices of goods experienced by consumers. It measures price changes by comparing, through time, the cost of a fixed basket of goods and services” (Statistics Canada, 2023). Throughout the last four decades, the price of goods has essentially been going up as highlighted in our Data 601 project, whereas the Average Income across Canada and across provinces has been going up, but not at the same rate as the CPI. Although most people understand that CPI and Income are correlated, many of us do not know just how statistically correlated the two variables are. 

What motivated this topic for both 601 and 602 was its relevance to every student and to every working adult, as well as seniors looking to retire. Money and the price of goods affects everyone and when people cannot afford the price of goods, it becomes a problem. Our group contains international and domestic students, and to be able to understand the basics of income and CPI provides us with insight on how we can effectively manage our finances better for the future.

Therefore, one objective of this project is to statistically determine the correlation between CPI and Average Income though linear regression while being able to utilize the created model to predict the future average income based on a theoretical future CPI value. This will require us to test the following hypothesis:

$$
\begin{eqnarray}
\text{H}_{0} &:& \ \text{There is no significant relationship between CPI and income.} \\
\text{H}_{A} &:& \ \text{There is a significant relationship between CPI and income.}
\end{eqnarray}
$$
Furthermore, the second statistical test will revolve around the comparison of means between four different provinces, which include Ontario (ON), British Columbia (BC), Nova Scotia (NS), and Prince Edward Island (PEI). These provinces were selected due to the higher income of ON and BC, whereas NS and PEI where chosen since they are relatively low in comparison. Ultimately, our objective is to see if there any income disparities that exist between these provinces. To do so, our hypothesis will be as follows:

$$
\begin{eqnarray}​
\text{H}_{0} &:& \ \text{The difference between the two means is equal to 0} \\​
\text{H}_{A} &:& \ \text{The difference between the two means is NOT equal to 0}​
\end{eqnarray}​
$$

## **Datasets**

We will focus on the use of two datasets in this report: **Income of individuals by age group, sex and income** as well as **Consumer Price Index, annual average, not seasonally adjusted** (Statistics Canada, 2023). Both datasets are available and accessible for the public through the Statistics Canada website which is a publisher of open data, and both are structured and tabular data with more columns than rows. 

*This licence is issued on behalf of His Majesty the King in Right of Canada, as represented by the Minister for Statistics Canada ("Statistics Canada") to you (an individual or a legal entity that you are authorized to represent) (Statistics Canada, 2023).*

For the purpose of this project, we simplified the data by only selecting the provinces that we wish to work on. This has been saved as "canada_data.csv."


```{r}
# Load the canada_data.csv file  
data = read.csv("canada_data.csv")

# Isolate Canada from data
Canada_data = data[data$Geography == "Canada", ]
Canada_data

# Plot CPI for Canada
ggplot(Canada_data, aes(x = Date, y = CPI)) + geom_line(color = "red") + labs(title = "CPI Over Past Four Decades")

# Plot Income for Canada
ggplot(Canada_data, aes(x = Date, y = Income)) + geom_line(color = "red") + labs(title = "Income Over Past Four Decades")

```
**From the above graph, it's clear that both CPI and Income have been increasing over the past four decades but it is not possible to tell how strong of a relation exists. Now that we've observed the trends in CPI and Income, let's get into the statistical analysis to uncover the nature of their relationship and test the hypotheses. In the first guiding question, we aim to see the correlation between the two variables.**

## **Guiding Question 1 – Is CPI correlated with Average Income for Canada?**


$$
\begin{eqnarray}
\text{H}_{0} &:& \ \text{There is no significant relationship between CPI and income.} \\
\text{H}_{A} &:& \ \text{There is a significant relationship between CPI and income.}
\end{eqnarray}
$$


```{r}
# Use ggplot to visualize CPI and Income from Canada_data dataframe
ggplot(Canada_data, aes(x = CPI, y = Income)) +  geom_point(size=1, col='blue') + xlab("CPI") + ylab("Income") + ggtitle("CPI to Income") +  geom_smooth(method="lm", color = "red")

# Use linear regression model for Canada data
model = lm(Income ~ CPI, data = Canada_data)
summary(model)
```
**The first graph, which is named "CPI to Income," shows that the two variables being compared are connected in a straight line. In other words, the graph demonstrates a linear relationship, but how strong is this relation? To statistically see the significance or strength in relation of the variables, a simple linear regression model will be created to find the correlation coefficient.**

**Before conducting a linear regression analysis, it is important to check the two conditions of normality as well as homoscedasticity.**

```{r}
# Run normality test and proof of homoscedasticity to see if the conditions for Linear Regression are met

leverage_values = hatvalues(model)
standardized_eis = rstandard(model)
absstandardized_eis = sqrt(abs(standardized_eis))

CPI_value = Canada_data$CPI
Income_value = Canada_data$Income
predictIncome = model$fitted.values
model_eis = model$residuals

# Create a dataframe for the model
model.df = data.frame (CPI_value, Income_value, predictIncome, model_eis, leverage_values, standardized_eis, absstandardized_eis)

# Check normal probability using normal probability plot 
ggplot(model.df, aes(sample = standardized_eis)) + stat_qq(col="blue", size = 1)  + stat_qqline(col='red') + ggtitle("Normal Probability Plot of Standardized Residuals")

# Check homoscedasticity
ggplot(model.df, aes(x = Income_value, y = standardized_eis)) +  geom_point(size=1, col='blue', position="jitter") + xlab("Income") + ylab("Standardized Risidualizes") + ggtitle("Plot with Income to Standardized Risiduals") + geom_hline(yintercept=0, color="red", linetype="dashed")

# Using stat_smooth instead of geom_hline
ggplot(model.df,aes(x = Income_value,y=standardized_eis)) + geom_point(size=1, col='blue', position="jitter") + geom_smooth(col="blue", linetype="dashed")
```

**When assessing the normality of the data, we observe that most data points closely follow the linear line. As a result, we can assume that the dataset we've created for the model is normally distributed.**

**When checking the condition of homoscedasticity, we want to ensure that the variance or spread of the residuals remains roughly the same or uniform as we move along the zero line.**

**Both assumptions are important for the linear regression model and tend to ensure that the results are reliable.**

```{r}
# Bootstrap for correlation coefficient to get confidence interval of the correlation value

# Set the seed for reproducibility
set.seed(123)

# Number of bootstrap samples
nsims = 1000

# Create an empty vector to store bootstrap correlations
bootstrap_correlations = numeric(nsims)

# Perform bootstrapping
for (i in 1:nsims) {
  sampled_data = Canada_data[sample(nrow(Canada_data), replace = TRUE), ]
  
  # Calculate the correlation between CPI and Average Income in the sampled data
  correlation = cor(sampled_data$CPI, sampled_data$Income)
  
  # Store the correlation in the vector
  bootstrap_correlations[i] = correlation
}

bootstrap_correlations.df = data.frame(bootstrap_correlations)


lower_bound = qdata(~bootstrap_correlations, 0.025, data = bootstrap_correlations.df)
upper_bound = qdata(~bootstrap_correlations, 0.975, data = bootstrap_correlations.df)

# 95% Bootstrap Confidence Interval
cat("Bootstrap 95% Confidence Interval:\n")
cat("Lower Bound:", lower_bound, "\n")
cat("Upper Bound:", upper_bound, "\n")

```

```{r}
# Plot histogram
ggplot(bootstrap_correlations.df, aes(x = bootstrap_correlations)) +
  geom_histogram(binwidth = 0.002, fill = "blue", color = "black") +
  geom_vline(xintercept = c(lower_bound, upper_bound), color = "red", linetype = "dashed", size = 1) + labs(title = "Bootstrap of correlation", x = "", y = "Frequency") 

```
**By using bootstrapping for the correlation coefficient, the 95% confidence interval obtained is 0.9174 to 0.9726. With this, we can be 95% confident that the true parameter, or the correlation coefficient for the linear regression model, lies in between this range. Below, we will conduct the linear regression model to determine the precise correlation coefficient value.**

```{r}
# HO = CPI and Income are independent (NOT related)
# HA = CPI and Income are NOT independent (Related)

# Use linear regression model for Canada
model = lm(Income ~ CPI, data = Canada_data)
summary(model)

# Standard error:
se_model = summary(model)$sigma 
se_model

# R-squared value:
rsquared(model)

# Sqaure root of R-sqaured value = will give us the same as the correlation coefficient above
sqrt(rsquared(model))

# Using Correlation 
correlation = cor (~CPI, ~Income, data = Canada_data)
correlation
```
**The linear model obtained gives us multiple statistics.** 

**The Formula for the Linear Model to help with prediction:**

$$
\widehat{{Income}}_i = 31103.85 + 145.39 \cdot CPI_i
$$
**Income represents the predicted or estimated income**

**CPI represents the Consumer Price Index which is a variable that we believe affects or influences the income**

**31103.85 is the intercept or the value of predicted income when the CPI is zero.**

**145.39 is the slope of the regression line, which represents how much the predicted income changes for a one-unit increase in CPI.**

**Multiple R-squared (0.9003): This coefficient tests how effectively the model shows the variance in income. Our high R-squared of 0.9003 implies that an estimated 90% of the variability in income can be accounted for by changes in CPI.**

```{r}
# Predict income and calculate the prediction interval for the a CPI value at 200

# Check CPI value at 136.0
predict(model, newdata = data.frame((CPI = 136.0)), interval="conf") 

# Check CPI value at 141.6
predict(model, newdata = data.frame((CPI = 141.6)), interval="conf") 

# Check the model for that exact point 
tail(Canada_data,4)
```


**We used the linear model we created to assess its accuracy with our dataset.For example, looking at a CPI of 136.0 (in 2019), the actual average income is 50700. From the model, we obtained a lower bound of 50167.76 and an upper bound of 51586.42, whereas the fit was 50877.09. This is realitvely close to the actual point in the data.**

**We also tried another point where CPI was at 141.6 (in 2021). The average income for Canadians during 2021 was 52800, but the model provided us with a lower bound of 50907.31 and an upper bound of 52475.25, whereas the fit was 51691.26 .In this case, the model did not closely match the actual average income. This discrepancy suggests that other factors may also influence average income, and relying only on the CPI for income estimation might not be sufficient. This is only a simple linear regression and therefore, there may be other variables that affect income.**


```{r}
# Predict income and calculate the prediction interval for the a CPI value at 200
predict(model, newdata = data.frame((CPI = 200)), interval = "predict")
```
**Although the model may not be completely accurate, we used the model to predict the average income if the CPI value was at 200. With this, we got a lower bound estimate of 57181.51 and an upper bound of 63182.78, whereas the fitted value was 60182.15. This indicates that when the CPI hits 200, the average income for Canadians may be around the lower and upper bounds.**

**This prediction not only demonstrates the flexibility and potential applications of our model but also shows the real-world significance of keeping a close eye on CPI fluctuations. It provides individuals, policymakers, and organizations with valuable insights into how economic changes could impact personal and collective financial well-being. As such, our study contributes to enhancing financial literacy and promoting informed decision-making on economic matters.**

## **Results**

**Guiding Question 1 – Is CPI correlated with Average Income for Canada**

**Our analysis of the correlation between the Consumer Price Index (CPI) and average income in Canada yielded significant insights. The statistical measures and findings are as follows:**

**The R-squared value, which measures the goodness of fit, is 0.900. This value is close to 1, indicating a strong relationship between CPI and average income. A higher R-squared value signifies a better fit of the model.**

**The correlation coefficient (sqrt of r-squared) is 0.949. This indicates a strong positive linear correlation, meaning that as CPI increases, average income also tends to increase. The closer the correlation coefficient is to 1, the stronger the positive correlation between the two variables.**

**P-Value: The P-value obtained is 2.2e^-16, which is less than an alpha of 0.05. This p-value means we can reject the null hypothesis in favor for the alternative which states that CPI and Income may have a significant relationship.**

**Through linear regression analysis, we can observe a strong positive linear correlation between the Consumer Price Index (CPI) and Income for Canada. The low p-value provides evidence to reject the null hypothesis and conclude that there is a significant relationship between these two variables.**

**Using the predict function, we can assume that when the CPI is at 200, the Average Income for Canadians will be in the range 57181.51 to 63182.78. The fitted value based on the theoretical model is 60182.15.**

## **Guiding Question 2 - Are there any income disparities between different provinces ?**

```{r}
# Compare the mean difference of income between two provinces
# Isolate data by province 

BC_data = data[data$Geography == "British Columbia", ]
BC_data

ON_data = data[data$Geography == "Ontario", ]
ON_data

PEI_data = data[data$Geography == "Prince Edward Island", ]
PEI_data

NS_data = data[data$Geography == "Nova Scotia", ]
NS_data
```


```{r}
# Plot the average income for each of the provinces we selected

averages = data %>%
  group_by(Geography) %>%
  summarise(AverageIncome = mean(Income, na.rm = TRUE))

ggplot(data = averages, aes(x = Geography, y = AverageIncome, fill = Geography)) + geom_bar(stat = "identity", position = "dodge") +labs(y = "Average Income", title = "Average Income by Province")


```
**From the graph above, it's evident that there are variations in average income across the four provinces chosen. Our objective is to statistically demonstrate this difference.**



$$
\begin{eqnarray}​
\text{H}_{0} &:& \ \text{The difference between the two means is equal to 0} \\​
\text{H}_{A} &:& \ \text{The difference between the two means is NOT equal to 0}​
\end{eqnarray}​
$$
**Please note the same Null and Alternative hypothesis will be used for all the mean difference comparisons below**

```{r}
# Check for normality for the average income in BC, ON, PEI, and NS

# Central Limit Theorem = if you take a sample mean from the population and we reach a certain point (n = 25 for example), we will reach a normal distribution

ggplot(BC_data, aes(sample = Income)) + stat_qq(col="blue", size = 1)  + stat_qqline(col='red') + ggtitle("Normal Probability Plot of Average Income for BC")

ggplot(ON_data, aes(sample = Income)) + stat_qq(col="blue", size = 1)  + stat_qqline(col='red') + ggtitle("Normal Probability Plot of Average Income for ON")

ggplot(PEI_data, aes(sample = Income)) + stat_qq(col="blue", size = 1)  + stat_qqline(col='red') + ggtitle("Normal Probability Plot of Average Income for PEI")

ggplot(NS_data, aes(sample = Income)) + stat_qq(col="blue", size = 1)  + stat_qqline(col='red') + ggtitle("Normal Probability Plot of Average Income for NS")
```

**When we create a plot of the average income for the four selected provinces, it's clear that most of them follow a normal distribution. Given this, we will treat each of these sets of values as a sample representing the entire population of each province. We will then use bootstrapping to calculate a confidence interval that estimates the true difference in means between these provinces.**


```{r}
# H0: The difference between the two means is equal to 0 
# HA: The difference between the two means is NOT equal to 0

observed_mean_difference = mean(ON_data$Income) - mean(BC_data$Income)
observed_mean_difference

n_ON = 41
n_BC = 41

# Create vector for the difference of means
nsims = 1000

sample_ON = numeric(nsims)
sample_BC = numeric(nsims)
bootstrap_mean_difference = numeric(nsims)

for (i in 1:nsims){
  sample_ON[i] = mean(sample(ON_data$Income, n_ON, replace = TRUE))
  sample_BC[i] = mean(sample(BC_data$Income, n_BC, replace = TRUE))
  bootstrap_mean_difference[i] = sample_ON[i] - sample_BC[i]
}
# Convert bootstrap data into a dataframe
bootstrap_mean_difference.df = data.frame(bootstrap_mean_difference)

# Plot bootstrap distribution
ggplot(data = bootstrap_mean_difference.df, aes(x = bootstrap_mean_difference)) + geom_histogram(binwidth = 100, fill = "blue", color= "black") + xlab("Boostrapping Mean Difference") + ggtitle("Bootstrap Distribution for Mean Difference") + geom_vline(xintercept = observed_mean_difference, color = "red")

# Use the qdata function
qdata(~bootstrap_mean_difference, data = bootstrap_mean_difference.df, c(0.025, 0.975))
```

**The 95% confidence interval calculated falls within the range of 1863.171 to 4617.073. This means that we can be 95% confident that the actual difference in average income between Ontario (ON) and British Columbia (BC) is somewhere within this interval.**

```{r}

# H0: The difference between the two means is equal to 0 
# HA: The difference between the two means is NOT equal to 0

# Using the t.test function 

t.test(ON_data$Income, BC_data$Income, data = Canada_data, conf.level = 0.95, alternative = "two.sided", var.equal = FALSE)

# The actual observed mean difference
observed_mean_difference

```

**By conducting a t-test, we have calculated a p-value of 2.105e-05 which is less than an alpha value of 0.05. This result provides strong statistical evidence for rejecting the null hypothesis, which suggests that the difference between the means is 0 Therefore, we can infer the alternative hypothesis which states that there is a significant difference in average income between Ontario (ON) and British Columbia (BC), or that the difference in means is not equal to 0. This is further supported by the fact that the true mean difference is equal to 3231.707.**

```{r}
# H0: The difference between the two means is equal to 0 
# HA: The difference between the two means is NOT equal to 0

observed_mean_difference = mean(NS_data$Income) - mean(PEI_data$Income)
observed_mean_difference

n_NS = 41
n_PEI = 41

# Create vector for the difference of means
nsims = 1000

sample_NS = numeric(nsims)
sample_PEI = numeric(nsims)
bootstrap_mean_difference = numeric(nsims)

for (i in 1:nsims){
  sample_NS[i] = mean(sample(NS_data$Income, n_NS, replace = TRUE))
  sample_PEI[i] = mean(sample(PEI_data$Income, n_PEI, replace = TRUE))
  bootstrap_mean_difference[i] = sample_NS[i] - sample_PEI[i]
}
# Convert bootstrap data into a dataframe
bootstrap_mean_difference.df = data.frame(bootstrap_mean_difference)

# Plot bootstrap distribution
ggplot(data = bootstrap_mean_difference.df, aes(x = bootstrap_mean_difference)) + geom_histogram(binwidth = 100, fill = "blue", color= "black") + xlab("Boostrapping Mean Difference") + ggtitle("Bootstrap Distribution for Mean Difference") + geom_vline(xintercept = observed_mean_difference, color = "red")

# Use the qdata function
qdata(~bootstrap_mean_difference, data = bootstrap_mean_difference.df, c(0.025, 0.975))
```

**The 95% confidence interval calculated falls within the range of 4718.415 to 8390.793 This means that we can be 95% confident that the actual difference in average income between Nova Scotia (NS) and Prince Edward Island (PEI) is somewhere within this interval.**

```{r}
# H0: The difference between the two means is equal to 0 
# HA: The difference between the two means is NOT equal to 0

# Using the t.test function 

t.test(NS_data$Income, PEI_data$Income, data = Canada_data, conf.level = 0.95, alternative = "two.sided", var.equal = FALSE)

# The actual observed mean difference
observed_mean_difference

```

**By conducting a t-test, we have calculated a p-value of 3.783e-09 which is less than an alpha value of 0.05. This result provides strong statistical evidence for rejecting the null hypothesis, which suggests that the difference between the means is 0 Therefore, we can infer the alternative hypothesis which states that there is a significant difference in average income between Nova Scotia (NS) and Prince Edward Island (PEI), or that the difference in means is not equal to 0. This is further supported by the fact that the true mean difference is equal to 6495.122**

```{r}
# H0: The difference between the two means is equal to 0 
# HA: The difference between the two means is NOT equal to 0

observed_mean_difference = mean(ON_data$Income) - mean(PEI_data$Income)
observed_mean_difference

# Create vector for the difference of means
nsims = 1000

sample_ON = numeric(nsims)
sample_PEI = numeric(nsims)
bootstrap_mean_difference = numeric(nsims)

for (i in 1:nsims){
  sample_ON[i] = mean(sample(ON_data$Income, n_ON, replace = TRUE))
  sample_PEI[i] = mean(sample(PEI_data$Income, n_PEI, replace = TRUE))
  bootstrap_mean_difference[i] = sample_ON[i] - sample_PEI[i]
}
# Convert bootstrap data into a dataframe
bootstrap_mean_difference.df = data.frame(bootstrap_mean_difference)

# Plot bootstrap distribution
ggplot(data = bootstrap_mean_difference.df, aes(x = bootstrap_mean_difference)) + geom_histogram(binwidth = 100, fill = "blue", color= "black") + xlab("Boostrapping Mean Difference") + ggtitle("Bootstrap Distribution for Mean Difference") + geom_vline(xintercept = observed_mean_difference, color = "red")

# Use the qdata function
qdata(~bootstrap_mean_difference, data = bootstrap_mean_difference.df, c(0.025, 0.975))
```

**Lastly, we wanted to see the difference in average income between Ontario (ON) and Prince Edward Island(PEI) only because the difference in average income is relatively large. By doing so, the 95% confidence interval obtained falls within the range of 14202.80 to 17987.44 This means that we can be 95% confident that the actual difference in average income between Ontario (ON) and Prince Edward Island(PEI) is somewhere within this interval.**


```{r}
# H0: The difference between the two means is equal to 0 
# HA: The difference between the two means is NOT equal to 0

# Using the t.test function 

t.test(ON_data$Income, PEI_data$Income, data = Canada_data, conf.level = 0.95, alternative = "two.sided", var.equal = FALSE)

# The actual observed mean difference
observed_mean_difference


```

**By conducting a t-test, we have calculated a p-value of 2.2e-16 which is less than an alpha value of 0.05. This result provides strong statistical evidence for rejecting the null hypothesis, which suggests that the difference between the means is 0 Therefore, we can infer the alternative hypothesis which states that there is a significant difference in average income between Nova Scotia (NS) and Prince Edward Island (PEI), or that the difference in means is not equal to 0. This is further supported by the fact that the true mean difference is equal to 16095.12**


## **Results**

**Guiding Question 2 - Are there any income disparities between different provinces ?**

The difference in average income for ON and BC is: $3231

The difference in average income for NS and PEI is: $6495

The difference in average income for ON and PEI is: $16095 

Overall, there exists statistically significant difference between the means for different provinces.This means we can assume that there is income disparity across these provinces


## **Things to Note**

We treated the population data provided by Statistics Canada as sample data

We are only looking at 2 variables, CPI and Average Income

We obtained p-value of 2.2e^-16 for three of the methods used. This is because R's limit is at that p-value. This means most of the time, we are in favor of the alternative hypothesis.

## **Conclusion**

**For Guiding Question 1 - Is CPI correlated with Average Income for Canada:**

The statistical analysis showed a strong positive linear correlation between the Consumer Price Index (CPI) and Income for Canada. The R-squared value of 0.900 and a correlation coefficient of 0.949 suggest that as CPI increases, average income also tends to increase. The low p-value of 2.2e^-16 provides strong evidence to reject the null hypothesis, indicating a significant relationship between CPI and Income.

**For Guiding Question 2 - Are there any income disparities between different provinces:**

By using bootstrapping methods and a t-test analysis, we can conclude that income disparity exists between various provinces. The differences in average income between Ontario (ON) and British Columbia (BC), Nova Scotia (NS) and Prince Edward Island (PEI), and Ontario (ON) and Prince Edward Island (PEI) were $3,231, $6,495, and $16,095, respectively. Futhermore, all p-values obtained were less than an alpha value of 0.05, which means we can reject our null hypothesis and infer the alternative that states that there is a significant difference in means, or that the mean is not equal to 0. These values indicate that there are income disparities across these provinces.

## **References**

Lord, Craig. (2023, January 6). Canadian workers’ wages are on the rise. Can they keep
  pace with inflation? Retrieved September 27, 2023, from
  https://globalnews.ca/news/9392311/canada-workers-wages-inflation/amp/

Statistics Canada. (n.d.). Consumer Price Index, annual average, not seasonally          adjusted. Retrieved September 17, 2023, from 
  https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=1810000501

Statistics Canada. (n.d.). Consumer price index portal. Retrieved September 17, 2023,    from  
  https://www.statcan.gc.ca/en/subjects-start/prices_and_price_indexes/consumer_price_indexes

Statistics Canada. (n.d.). Income of individuals by age group, sex and incomesource.     Retrieved September 17, 2023, from 
  https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=1110023901&pickMembers%5B0%5D=1.1&pickMembers%5B1%5D=2.1&pickMembers%5B2%5D=3.1&pickMembers%5B3%5D=4.1&cubeTimeFrame.startYear=1981&cubeTimeFrame.endYear=2021&referencePeriods=19810101%2C20210101
